Advances in medicine, materials science, computer science and numerical methods have brought the ideal of a patient-specific implant therapy supported with accurate predictions from digital twins within reach. Upcoming techniques like machine learning and artificial intelligence enable the processing of enormous amounts of data and mathematical models in combination with numerical methods help in creating a better understanding of the highly complex multi-physical processes. This cumulative thesis presents three approaches to describe the behavior of implant material using continuum modelling in combination with the finite element method. The first approach models the drug release of a diffusion-controlled drug delivery system, which consists of a drug loaded reservoir surrounded by a porous membrane. The model aims to support the fabrication process of the drug delivery system by predicting the drug concentration profile over time in the patient, depending on the geometric parameters, porosity and drug loading of the implant. The results from the numerical predictions are compared with experimental measurements and enable the identification of ideal tuning options for a patient-specific therapy. The second approach models the complex mechanical behavior of a metallic implant material exhibiting highly anisotropic mechanical properties due to twinning as an additional plastic deformation mechanism. The model includes twinning with a volume fraction transfer scheme, which allows to include twins without explicitly resolving individual twins, which opens the possibility for simulations on a larger scale. An efficient numerical treatment of slip deformation in newly formed twins is obtained by an newly developed efficient algorithm, which significantly reduces the number of unknowns and thus makes treatment of secondary plasticity feasible for this approach. The model is verified by comparison to experimental results for single and polycrystal magnesium stress-strain measurements. The third approach is a framework to model the multi-physical processes in corrosion of metallic implant materials. The model uses the variational generalized standard materials framework and couples mechanical deformation, chemical swelling, multi-component diffusion, chemical reactions, electric fields, electric currents, multiple phases and phase transformations. Furthermore, the developed framework ensures fundamental laws, such as the balance of mass, charge, momentum and consistency with the second law of thermodynamics. Finite element simulations demonstrate the capability to describe the coupled electro-chemo-mechanical processes involved e.g. in the formation and dissolution of a degradation layer. All three models demonstrate the ability to improve the understanding of implant material behavior and may serve as tools for the optimization of medical implant fabrication processes and are therefore a few steps on the road towards full digital twins. 