I feel blessed and grateful for all the support from amazing people who have accompanied me along the way and I would like to express my sincere gratitude.\\

First of all, I would like to thank Prof. Dr. Rainer Adelung for giving me the opportunity to persue my PhD in his group, for all his support, guidance and for the freedom to research and develop independently. I have always been fascinated by your creativity, endless ideas, scientific enthusiasm and inspiring view of things.\\ 

I would also like to thank Dr. Fabian Schütt for his tremendous support over the past few years. I deeply appreciate everything you have done for me. Thank you for guiding, encouraging and pushing me! I have learned an enormous amount from you, both scientifically and personally. You manage to combine professional and personal leadership, creating a basis of trust that allows everyone to grow. It is so much easier to stay motivated in difficult times in a pleasant working environment with the perfect balance between work and fun.\\

My sincere thanks also go to Dr. Sören Kaps for all his support with setups and programming, for scientific discussions and for all his efforts in our group, basically being a rock for everyone. Big thank you also goes to Jörg Bahr for invaluable help in the lab and with setups as well as to Dr. Jürgen Carstensen for scientific discussions.\\

My deepest gratitude also goes to our secretary's office, Vivian Wehr, Beate Minten and formerly Katrin Brandenburg for their management and administration work and their irreplaceable support with orders, travels and more.\\

I also want to thank the most FUN working group I was lucky to be part of, including Florian Rasch, Leonard Siebert, Lena Saure, Christine Arndt, Sandra Hansen, Beate Minten, Vivian Wehr, Katrin Brandenburg, Jörg Bahr, Martina Baum, Fabian Schütt, Haoyi Qiu, Anna Gapeeva, Heather Cavers, Jan-Martin Wagner, Monja Gronenberg, Kerstin Meurisch, Tehseen Riaz, Peter Sommer, Oleg Lupan, George Popkirov, Jürgen Carstensen, Sören Kaps, Roshani Madurawala, Pia Holtz, Lukas Zimoch, Barnika Chakraborty, Martha Gerhardt, Erik Greve, Jannik Rank, Jakob Offermann, Deik Petersen, Chima Obobi Kalu, Catarina Schmidt, Helge Krüger, Armin Reimers, Philipp Schadte, Jan-Ole Stern, Maik-Ivo Terasa.\\  

I would also like to acknowledge the work of my thesis and research assistant students Caprice Mohr, Roshani Madurawala, Jonas Fiedler, Maike Gremmel, Philipp Kloth, Roman Kurberg and Erik Greve. This work would not have been possible without your help.\\

A big thank you also goes to the former best office ``The Office A-241'' including the wall of fame members Roshani, Armin, Morten, Fabian and Lena.\\ 

As part of the research training group ``Materials for Brain'' I would also like to acknowledge the support of the PIs, coordinators, collaborators especially Prof. Dr. Dr. Janka Held-Feindt and Dr. Carolin Kubelt, and of the PhDs including Lisa Hanke, Duygu Dengiz, Luise Schlotterose, Frowin Ellermann, Isil Ünal, Ankit Mishra, Torge Hartig, Jan Dittmann, Rosa Rojas, Mishal Khan, Krathika Bhat, Dana Hellmold and Eva Peschke. It has been a great time, thank you!\\

I would also like to thank Prof. Jaana Vapaavuori's group at Aalto University for welcoming me so warmly during my research stay abroad. Special thanks to Pedro and Matteo for making my stay especially pleasant.\\

Special thanks go to Lena and Tine for being the most amazing friends. You are always there for me and without you I would not have gone through with it. Thank you for all the fun times!  Same holds for Rosh - thanks for always being there for me and cheering me up with your positive vibes. A big thank you also goes to Dana, who always manages to make me feel good with her positive energy and I know, more city trips are waiting for us! Big thanks also goes to Armin who really has his heart in the right place. I feel so blessed and thankful to have such wonderful friends. You make life worth living. \\ 

Finally, I would like to thank my family for their endless support and Jan for loving me for who I am. 





