\vspace{1cm}
Hiermit erkläre ich an Eides statt, die Dissertation ``Bioinspired functional interpenetrating composites by micro- and nanostructuring of soft polymers'' eigenständig, d.h. insbesondere selbständig und ohne Hilfe eines kommerziellen Promotionsberaters, angefertigt und keine anderen als die von mir angegebenen Quellen und Hilfsmittel verwendet zu haben. Ich erkläre außerdem, dass die Dissertation weder in gleicher noch in ähnlicher Form bereits in einem anderen Prüfungsverfahren vorgelegen hat und unter Einhaltung der Regeln guter wissenschaftlicher Praxis der Deutschen Forschungsgemeinschaft entstanden ist. Des Weiteren erkläre ich, dass mir bislang kein akademischer Grad entzogen wurde.

\vspace{2cm}
\rule{5cm}{0.2pt} \hspace{4cm} \rule{5cm}{0.2pt}\\ 
\hspace*{1.5cm} Ort, Datum \hspace{7cm} Unterschrift
\vspace{2cm}

I hereby confirm that the dissertation ``Bioinspired functional interpenetrating composites by micro- and nanostructuring of soft polymers'' is the result of my own work. I did not receive any help or support from commercial consultants. All sources and/or materials applied here are listed and specified in the thesis. Furthermore, I confirm that this thesis has not yet been submitted as part of another examination process, neither in identical nor in similar form, and has been prepared subject to the Rules of Good Scientific Practice of the German Research Foundation. Furthermore, I declare that no academic degree has been withdrawn from me in the past.

\vspace{2cm}
\rule{5cm}{0.2pt} \hspace{4cm} \rule{5cm}{0.2pt}\\ 
\hspace*{1.5cm} Place, Date \hspace{7.2cm} Signature
